Wavelet Spatio-Temporal Change Detection Method for Multi-Temporal SAR Images

### 2021-12-08 tex/paper.wecs/wecs_tgrs__trans06dez21.tex
atualizacao (08dez21)

@@

\subfigure[Ground truth change/non-change samples]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/Samples.pdf}\label{figImgSentinelROIs}}

@@

%-----------------------
\begin{figure}[htp!]
\centering
\includegraphics[scale=.2]{../../figs/forest_vSumDifCoefSq}\hspace{-.5cm}
\caption{Plot of $\vd(m)$, $m=1,\ldots,85$ with orange horizontal line indicating two times its median absolute deviation.}
\label{F:forest_wecs}
\end{figure}

@@

\mbox{
\subfigure[$m=25$]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/forestChange_m25.pdf}\label{figImgSentinel2015}} 
\subfigure[$m=27$]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/forestChange_m27.pdf}\label{figImgSentinel2017}}
}

\mbox{
\subfigure[$m=30$]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/forestChange_m30.pdf}\label{figImgSentinel2015}} 
\subfigure[$\overline{\mathcal{I}}$]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/forestChange_mean.pdf}\label{figImgSentinel2017}}
}

@@

\mbox{
\subfigure[Ground truth samples]{\includegraphics[width=0.23\textwidth]{../../figs/forest_change}\label{figResForestWecs}} 
\subfigure[ROC]{\includegraphics[width=0.23\textwidth]{../../figs/forest_roc_change}\label{figResForestAggreg}} 
}

\caption{
Change points in space of the forest data. 
(a) Regions (in white) where changes should be detected.
(b) ROC curve for detection of changing regions. 
}\label{F:forest_roc_wecs_agg___TEMP}
\end{figure}

\mbox{
\subfigure[WECS \textcolor{red}{(Temp. img)}]{\includegraphics[width=0.23\textwidth]{../../figs/forest_wecs_abscorr}\label{figResForestWecs}} 
\subfigure[Log.Aggreg. \textcolor{red}{(Temp. img)}]{\includegraphics[width=0.23\textwidth]{../../figs/forest_aggreg_ratios}\label{figResForestAggreg}} 
}

\mbox{
\subfigure[Change map -- WECS \textcolor{red}{(Temp. img)}]{\includegraphics[width=0.23\textwidth]{../../figs/forest_wecs_change_space}\label{figResForestWecs}} 
\subfigure[Change map -- Aggreg. \textcolor{red}{(Temp. img)}]{\includegraphics[width=0.23\textwidth]{../../figs/forest_aggreg_change_space}\label{figResForestAggreg}} 
}

\caption{
Change points in space of the forest data. 
%(a) Regions (in white) where changes should be detected.
%(b) ROC curve for detection of changing regions. 
(a) Matrix of absolute correlations obtained with WECS.
(b) Change measures from aggregation of absolute differences. 
(c) Change regions detected by highlighting the $[N/\log N]$ largest correlations in $\vR$ ($N$ denoting the image's dimension). 
(d) Change regions detected using aggregated absolute differences and Otsu's thresholding.}\label{F:forest_roc_wecs_agg}
\end{figure}

\begin{table}
\caption{Accuracy measures $F_1$-score, Precision ($\mathrm{Pr}$) and Recall ($\mathrm{Re}$) computed from detection of changing regions in the forest data using WECS (taking the $[N/\log N]$ largest correlations as corresponding to change) and the aggregation of absolute differences with Otsu and Kittler-Illingworth's (KI) thresholds.}
\centering
\begin{tabular}{c|ccc}
\hline
  & Aggregated - Otsu & Aggregated - KI & WECS \\
\hline
$F_1$-score & 0.2231 & 0.2163 & 0.3253 \\
$\mathrm{Pr}$ & 0.1369 & 0.1296 & 0.2390 \\
$\mathrm{Re}$ & 0.6022 & 0.6526 & 0.5094 \\
\hline
\end{tabular}
\label{T:forest_accuracy}
\end{table}

>>>>

\usepackage{float}

@@

\subfigure[Ground truth change/non-change samples]{\includegraphics[width=0.3\textwidth]{../../qgis/maps/SamplesRev.pdf}\label{figImgSentinelROIs}}

@@

%-----------------------
\begin{figure}[htb!]
\centering
\includegraphics[width=0.485\textwidth]{../../graphs/LineInstants_1-30-59.pdf}
\caption{Plot of $\vd(m)$ for $m=1,\ldots,85$. The three larger deviations occurs at $m$ equivalent to $25$, $27$ and $30$.
%with orange horizontal line indicating two times its median absolute deviation.
}
\label{F:forest_wecs}
\end{figure}

@@

\mbox{
\subfigure[$m=1$]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/X_1.pdf}\label{figImgSentinel2015}} 
\subfigure[$m=30$]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/X_30.pdf}\label{figImgSentinel2017}}
}

\mbox{
\subfigure[$m=59$]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/X_59.pdf}\label{figImgSentinel2015}} 
\subfigure[$\overline{\mathcal{I}}$]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/X_mean.pdf}\label{figImgSentinel2017}}
}

@@

%%-----------------------
%\begin{figure}[hbt]
%\centering
%
%\mbox{
%\subfigure[Ground truth samples]{\includegraphics[width=0.23\textwidth]{../../figs/forest_change}\label{figResForestWecs}} 
%\subfigure[ROC]{\includegraphics[width=0.23\textwidth]{../../figs/forest_roc_change}\label{figResForestAggreg}} 
%}
%
%\caption{
%Change points in space of the forest data. 
%(a) Regions (in white) where changes should be detected.
%(b) ROC curve for detection of changing regions. 
%}\label{F:forest_roc_wecs_agg___TEMP}
%\end{figure}

%%-----------------------
%\begin{figure}[hbt]
%\centering
%
%\mbox{
%\subfigure[WECS \textcolor{red}{(Temp. img)}]{\includegraphics[width=0.23\textwidth]{../../figs/forest_wecs_abscorr}\label{figResForestWecs}} 
%\subfigure[Log.Aggreg. \textcolor{red}{(Temp. img)}]{\includegraphics[width=0.23\textwidth]{../../figs/forest_aggreg_ratios}\label{figResForestAggreg}} 
%}
%
%\mbox{
%\subfigure[Change map -- WECS \textcolor{red}{(Temp. img)}]{\includegraphics[width=0.23\textwidth]{../../figs/forest_wecs_change_space}\label{figResForestWecs}} 
%\subfigure[Change map -- Aggreg. \textcolor{red}{(Temp. img)}]{\includegraphics[width=0.23\textwidth]{../../figs/forest_aggreg_change_space}\label{figResForestAggreg}} 
%}
%
%\caption{
%Change points in space of the forest data. 
%%(a) Regions (in white) where changes should be detected.
%%(b) ROC curve for detection of changing regions. 
%(a) Matrix of absolute correlations obtained with WECS.
%(b) Change measures from aggregation of absolute differences. 
%(c) Change regions detected by highlighting the $[N/\log N]$ largest correlations in $\vR$ ($N$ denoting the image's dimension). 
%(d) Change regions detected using aggregated absolute differences and Otsu's thresholding.}\label{F:forest_roc_wecs_agg}
%\end{figure}

%-----------------------
\begin{figure}[h!]
\centering

\mbox{
\subfigure[WECS-KI]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/WECS-KI.pdf}\label{figResChange1}} 
\subfigure[WECS-OT]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/WECS-OT.pdf}\label{figResChange2}}
}

\mbox{
\subfigure[ECS-OT]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/ECS-OT.pdf}\label{figResChange3}} 
\subfigure[TAAD-KI]{\includegraphics[width=0.23\textwidth]{../../qgis/maps/TAAD-KI.pdf}\label{figResChange4}}
}

\caption{
\textcolor{red}{Change points in space of the forest data. 
%(a) Regions (in white) where changes should be detected.
%(b) ROC curve for detection of changing regions. 
(a) Matrix of absolute correlations obtained with WECS.
(b) Change measures from aggregation of absolute differences. 
(c) Change regions detected by highlighting the $[N/\log N]$ largest correlations in $\vR$ ($N$ denoting the image's dimension). 
(d) Change regions detected using aggregated absolute differences and Otsu's thresholding.}}
%\label{F:forest_roc_wecs_agg}
\label{figSentinelResults}
\end{figure}

%\begin{table}
%\caption{Accuracy measures $F_1$-score, Precision ($\mathrm{Pr}$) and Recall ($\mathrm{Re}$) computed from detection of changing regions in the forest data using WECS (taking the $[N/\log N]$ largest correlations as corresponding to change) and the aggregation of absolute differences with Otsu and Kittler-Illingworth's (KI) thresholds.}
%\centering
%\begin{tabular}{c|ccc}
%\hline
%  & Aggregated - Otsu & Aggregated - KI & WECS \\
%\hline
%$F_1$-score & 0.2231 & 0.2163 & 0.3253 \\
%$\mathrm{Pr}$ & 0.1369 & 0.1296 & 0.2390 \\
%$\mathrm{Re}$ & 0.6022 & 0.6526 & 0.5094 \\
%\hline
%\end{tabular}
%\label{T:forest_accuracy}
%\end{table}

\begin{table}[H]
\caption{Inserir...  variances are multiplied by $\times 10^{-5}$}\label{tabAccExpSentinel}
\centering

\begin{tabular}{ccccccc}
\thickhline
 & \multicolumn{2}{c}{\textbf{WECS}} & \multicolumn{2}{c}{\textbf{ECS}} & \multicolumn{2}{c}{\textbf{TAAD}}\tabularnewline
\hline 
Threshold & OT & KI & OT & KI & OT & KI\tabularnewline
F1-Score & 0.940 & 0.876 & 0.6189 & 0.661 & 0.798 & 0.778\tabularnewline
kappa & 0.818 & 0.698 & 0.535 & 0.513 & 0.244 & 0.284\tabularnewline
var. of kappa & 6.90 & 3.43 & 1.91 & 1.72 & 0.76 & 0.91 \tabularnewline
\thickhline
\end{tabular}

\end{table}

%-----------------------
\begin{figure}[hbt]
\centering
\includegraphics[width=0.485\textwidth]{../../graphs/TPTNs.pdf}
\caption{Percentages of True/False Positives (TP/FP) and True/False Negatives (TN/FN) relative to change (Positive) and non-change (Negative) reference samples.}\label{figAE}
\end{figure}
